---
title: "Code Related to Figure 1A"
author: "Ashley Doane"
date: "2022-11-27"
output: html_document
---
## QQ-Plots

To produce a pdf file with a qq plot showing BTG1, clone this repository, ensure the required packaged are installed, and run `R CMD BATCH makeQQplot.R`.  To execute code interactively, follow tutorial below.

### Code
Here we will generate a quantile-quantile plot of observed p-values and p-values computed from a uniform distribution.






```{r, warning=FALSE,include=FALSE, echo=TRUE }
require(data.table)
require(fishHook)
require(cowplot)


```


```{r}

#'  @name ggqq
#'  @description
#'  Function to plot a quantile-quantile plot from a vector of p-values.  Points are highlighted and gene labels printed from a character vector of gene names.  Values other than "" will be highlighted/shown. 
#'  are specified by a character vector of gene names, where  
ggqq <- function(ps, symbol, ci = 0.95, splitx=3.5, pcolor) {
    require(ggrepel)
  theme_set(theme_cowplot())
    N  <- length(ps)
    df <- data.frame(
        observed = -log10(sort(ps)),
        expected = -log10(1:N / N),
        clower   = -log10(qbeta(ci,     1:N, N - 1:N + 1)),
        cupper   = -log10(qbeta(1 - ci, 1:N, N - 1:N + 1)),
        symbol   = symbol
    )
    log10Pe <- expression(paste("Expected -log"[10], plain(P)))
    log10Po <- expression(paste("Observed -log"[10], plain(P)))
    ggplot(df, aes(expected,observed,label=symbol)) +
        geom_point(aes(expected, observed), shape = 16, 
                   color = ifelse(pcolor == "", "black", "red")) +
        geom_abline(intercept = 0,
                    slope = 1,
                    alpha = 0.5) +
        geom_line(aes(expected, cupper), linetype = 2) +
        geom_line(aes(expected, clower),
                  linetype = 2,
                  color = 'red') +
        xlab(log10Pe) +
        ylab(log10Po) +
        #coord_cartesian(xlim = c(0, max(df$observed)), ylim=c(0,max(df$observed))) +
        #xlim(0, 4.5) +
        geom_text_repel(
            data = subset(df, (expected > splitx & observed > 1)),
            nudge_x      =  6 - subset(df, (expected > splitx & observed > 1))$expected,
            direction    = "y",
            hjust        = 0,
            max.time = 5, max.iter = 100000,
            segment.size = 0.2) +
        geom_text_repel(
            data = subset(df, (expected <= splitx & observed > 1)),
            nudge_x      =  1 - subset(df, (expected <= splitx & observed > 1 ))$expected,
            direction    = "y",
            nudge_y =  10,
           # nudge_y =  1 + subset(df, (expected <= splitx & observed > 1 ))$observed,
            hjust        = 1,
            max.time = 5, max.iter = 100000,
            segment.size = 0.2)

}

plotQQ <- function(result.df) {
  result.df$plotSymbol <- ""
  result.df$plotSymbol[1:20] <- result.df$name[1:20]
  result.df[, plotcolor := ifelse(fdr<=0.001, name, "")]     
  ggqq(result.df$p, symbol = result.df$plotSymbol, pcolor = result.df$plotcolor)
}

```



#### Read file with FishHook results. 
```{r}
require(data.table)
require(fishHook)
require(ggrepel)

result.df <- fread("./fishHook.results.tsv")




```

#### Preview the file

```{r}
result.df
```


#### Set FDR thresholds for point color and generate plot with gene labels for top 20 hits.
```{r}



plotQQ(result.df)

```